A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2015-10-06 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Use double spacing, as required by journal
Create title page, as required by journal

@@

% ToDo: uncomment this post-acceptance: the journal uses double blind reviewing.
% \author{Annika Siders\inst{1} \and Bruno Woltzenlogel Paleo\inst{2}}

% \authorrunning{A.\~Siders \and B.\~Woltzenlogel Paleo}

% \institute{
%   University of Helsinki, Finland\\
%   \email{annika.siders@helsinki.fi}
%   \and 
%   Vienna University of Technology, Austria ; Australian National University \\
%   \email{bruno.wp@gmail.com} 
% }

\author{}
\authorrunning{}
\institute{}

@@

\begin{abstract}
This paper presents two detailed formalizations of ontological arguments in a simple natural deduction calculus. The first formal proof closely follows the hints in Scott's manuscript about G\"odel's argument and fills in the gaps, thus verifying its correctness. The second formal proof improves the first one, by: relying on the weaker modal logic {\bf KB} instead of the stronger modal logic {\bf S5};  and by avoiding the introduction of the equality predicate. The second proof is also technically shorter than the first one, because it eliminates unnecessary detours and uses Axiom 1 for the positivity of properties only once.
\end{abstract}

>>>>

\usepackage{setspace}
\doublespacing

@@

\author{Annika Siders\inst{1} \and Bruno Woltzenlogel Paleo\inst{2,3}}

\authorrunning{A.\~Siders \and B.\~Woltzenlogel Paleo}

\institute{
  \email{annika.siders@helsinki.fi} \\
  +358 2941 29241
  Department of Philosophy \\
  University of Helsinki\\
  P.O. Box 24 (Unioninkatu 40 A) \\
  Finland \\[2em]
  \and 
  \email{bruno@logic.at}
  Theory and Logic Group \\ 
  Vienna University of Technology \\ 
  Austria \\[2em]
  \and
  \email{bruno.woltzenlogel.paleo@anu.edu.au}
  Logic and Computation Group \\
  College of Engineering and Computer Science \\
  Australian National University \\
  Australia
}

@@

\clearpage

\title{A Variant of G\"{o}del's Ontological Proof \\
in a Natural Deduction Calculus}
\author{}
\authorrunning{}
\institute{}
\maketitle

\begin{abstract}
This paper presents two detailed formalizations of ontological arguments in a simple natural deduction calculus. The first formal proof closely follows the hints in Scott's manuscript about G\"odel's argument and fills in the gaps, thus verifying its correctness. The second formal proof improves the first one, by relying on the weaker modal logic {\bf KB} instead of the stronger modal logic {\bf S5}; and by avoiding the introduction of the equality predicate. The second proof is also technically shorter than the first one, because it eliminates unnecessary detours and uses Axiom 1 for the positivity of properties only once.
\end{abstract}
